Designing Turk Experiments for Visual Statistical Inference

### 2013-06-12 paper_turk.tex
updated introduction

%\usepackage{amsmath, amssymb, fullpage, amsthm, array, algorithm2e,graphicx}
\usepackage{graphicx}
\usepackage{url}
\usepackage[colorlinks=true, citecolor=blue, linkcolor=blue]{hyperref}

@@

The power of visual test is studied by Majumder \cite{majumder:2013} and it is revealed that power could be as good as conventional test and some times even better. But where the conventional test does not exists, visual inference could be the only inferential procedure without compromising a lot in power.

These developments open up a whole new area of statistical research where lineups need to be evaluated by human observer. There are some reasons a researcher needs to evaluate lineups. One is to assess the power of the visual test \cite{heike:2012} for different visual test statistics. The another reason would be to make decision based on the lineup, i.e., to use lineup protocol in practical application \cite{niladri:2012}. Other reasons could be to present the results of the conventional test with visual tools such as lineup.

@@

The power of visual test can be obtained theoretically \cite{majumder:2013} under some conditions. In general it is hard to obtain explicitly with a mathematical formula since it is very much dependent on individual observation. One approach to estimate the power is to recruit observers to evaluate lineups obtained in known controlled situation \cite{majumder:2013}. It is better to get observers as diverse as possible without being much concerned about the observers' formal training about statistical graphics.

@@

@@

The web application is designed such a way that it still produces simple task for the worker who are used to doing so from MTurk. But it gives many flexibilities to the researcher who need lineups to be evaluated as per complex experimental requirement.

@@

\bibliographystyle{plain}
\bibliography{references}

>>>>

%\usepackage{amsmath, amssymb, fullpage, amsthm, array, algorithm2e,graphicx}
\usepackage{graphicx}
\usepackage{url}
\RequirePackage{natbib}
\usepackage[colorlinks=true, citecolor=blue, linkcolor=blue]{hyperref}

@@

The power of visual test is studied by \cite{majumder:2013} and it is revealed that power could be as good as conventional test and some times even better. But where the conventional test does not exists, visual inference could be the only inferential procedure without compromising a lot in power.

These developments open up a whole new area of statistical research where lineups need to be evaluated by human observer. There are some reasons a researcher needs to evaluate lineups. One is to assess the power of the visual test \citep{heike:2012} for different visual test statistics. The another reason would be to make decision based on the lineup, i.e., to use lineup protocol in practical application \citep{niladri:2012}. Other reasons could be to present the results of the conventional test with visual tools such as lineup.

@@

The power of visual test can be obtained theoretically under some assumptions on individual behavior which was evident from experimental studies \citep{majumder:2013}. In general it is hard to obtain explicitly with a mathematical formula since it is very much dependent on individual observation. One approach to estimate the power is to recruit observers to evaluate lineups obtained in known controlled situation. Individual differences in the abilities of correct evaluations of lineup were observed. But Observer's education levels do not seem to have significant effect on performances. Thus it is better to get observers as diverse as possible without being much concerned about the observers' formal training about statistical graphics.

This poses a new challenge to researcher to recruit people from a diverse pool of population. Cost, time, data accuracies and convenience are some of the issues that need to be dealt with. Moreover, those who need to make statistical decision based on lineup plot will need a system that could provide an easy solution to this challenge.  This paper provides a complete solution to this by presenting plans for experimental design, developing an web application to recruit people from Amazon Mechanical Turk (MTurk) web site and providing detailed task management while doing an experiment through MTurk.

@@

\subsection{Getting Turk Workforce}

@@

The web application is designed such a way that it still produces simple task for the worker who are used to doing so from MTurk. But it gives many flexibilities to the researcher who need lineups to be evaluated as per complex experimental requirement. The design of this application allows recruiting people from any source not necessarily just from MTurk. Also once the application is hosted, any number of experiments can be done through this without changing the core of this application.

The next direction of this work is to make a complete package so that anyone can reproduce this web application, customize according to their need and run the MTurk experiments as part of their research that involves lineups. This would save lot of time which researcher can use focusing on their actual research. This would also help lineup protocol to be used frequently since it would provide an ease of its use in making inferential decisions.

We also intend to set up a web application for public use where researcher can put their lineup for online evaluation. The observer could be recruited from MTurk or any other source including local lab participants.

@@

%\bibliographystyle{plain}
\bibliographystyle{asa}
\bibliography{references}
